### 2020-06-12 Documents/ESA/sections/ResearchSummary.tex
Updated Write Up and ESA

\documentclass{article}

\usepackage[margin=2cm]{geometry}
\usepackage{amsmath,amsfonts}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{color}
\newcommand\fb[1]{\textcolor{blue}{FB: #1}}

\title{Derivation Write Up}
\author{Aamal Hussain}

@@

\maketitle

\fb{the bibfile is missing.}

	\section{Introduction} % (fold)
	\label{sec:introduction}

	\begin{itemize}
			\item For use in Multi-Agent Reinforcement Learning
			\item Requirement to get some desired behaviours out of the system (e.g. conforming to
			predefined values or constraints)
			\item For this, it is required that we are able to predict the outcome of the learning
			behaviour
			\item Work done on determining the dynamics of MARL gives an indication of what
			solutions an algorithm will produce
			\item We can use this, alongside stability theory, to understand the nature of the games
			which result in stable behaviours and which result in chaotic behaviours.
			\item Largely follows the work presented by Sanders et al. However, whilst they consider
			EWA, we consider Q-Learning, which is more popular in RL communities.
	\end{itemize}

	\subsection{Problem Statement} % (fold)
	\label{sub:problem_statement}

	Given a particular learning algorithm and game, is it possible to determine whether the game is
	likely to reach a unique fixed point or exhibit more complex behaviour? What are the factors
	which affect this resulting behaviour?

	% subsection problem_statement (end)

	\subsection{Objectives and Scope} % (fold)
	\label{sub:objectives_and_scope}

	Analyse the stability of Multiagent Q-Learning on iterated games.

	Assumptions:

	\begin{itemize}
		\item Focuses on stateless games
		\item Homogeneous agents
		\item Discrete action spaces, with large number of actions.
		\item Small, finite number of agents.
	\end{itemize}

	The work by Sanders et al. considers agents who have these same assumptions, but learn with a
	reduced version of the Experience Weighted Attraction algorithm. For the Reinforcement Learning
	community, it is of interest to consider the question of stability from the point of view of
	agents who follow the popular Q-Learning algorithm.

 \fb{you might discuss in which way any of the points above differs from the relevant reference.}

	% subsection objectives_and_scope (end)

	% section introduction (end)

	\section{Derivation} % (fold)
	\label{sec:derivation}

        \fb{it would be good to have a overall description of the goal of the derivation.}

@@

	\begin{equation}
	\begin{split}
	\label{eqn::moveddisorder}
		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i
		\sum_i \int dt[\hat{x}_i
		(\frac{\dot{x_i}(t)}{x_i(t)}
			- \tilde{\alpha} \rho_{x, i}(t)+ h_{x, i}(t))]) 
			\\
			\times exp(i \sum_i \int dt[\hat{y}_i
		(\frac{\dot{y_i}(t)}{y_i(t)} 
			- \tilde{\alpha} \rho_{y, i}(t) + h_{y, i}(t))])\\
			\times exp(i \sum_i
		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))])\\
		\times exp(i \sum_i \int dt[- \hat{x}_i \alpha \tilde{\tau} \sum_{j} a_
			{ij} 
			y_j +
			\hat{x}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j - \hat{y}_i
			\alpha 
			\tilde{\tau} \sum_{j} b_
			{ij} 
			x_j +
			\hat{y}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j]).
	\end{split}
	\end{equation}
	The only difference between (\ref{eqn::generatingfunctional}) and (\ref{eqn::moveddisorder}) is
	that we moved the term \fb{which one exactly?} containing the quenched disorder into a separate exponential. Since our
	aim is to take an average over all possible realisations of this disorder, we will only need to
	focus on the last exponential which we rewrite as

@@

	It should be noted that we have changed some of the subscripts on the terms. Since these terms
	are all multiplied together and we sum over the subscripts, the letters we choose are of no
	importance and we can exchange them freely \fb{perhaps some more justification might be helpful}. We will define both exponentials in $Q$ as $Q_1$ and
	$Q_2$ respectively.

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run1.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2.png}
	\caption{$\alpha = 0.2$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2_Run_2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}

@@

% section numerical_simulations (end)
\end{document}

>>>>

\documentclass[.../main.tex]{subfiles}

@@

@@

	\begin{equation}
	\begin{split}
	\label{eqn::moveddisorder}
		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i
		\sum_i \int dt[\hat{x}_i
		(\frac{\dot{x_i}(t)}{x_i(t)}
			- \tilde{\alpha} \rho_{x, i}(t)+ h_{x, i}(t))]) 
			\\
			\times exp(i \sum_i \int dt[\hat{y}_i
		(\frac{\dot{y_i}(t)}{y_i(t)} 
			- \tilde{\alpha} \rho_{y, i}(t) + h_{y, i}(t))])\\
			\times exp(i \sum_i
		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))])\\
		\times exp(i \sum_i \int dt[- \hat{x}_i \alpha \tilde{\tau} \sum_{j} a_
			{ij} 
			y_j +
			\hat{x}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j - \hat{y}_i
			\alpha 
			\tilde{\tau} \sum_{j} b_
			{ij} 
			x_j +
			\hat{y}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j]).
	\end{split}
	\end{equation}
	The only difference between (\ref{eqn::generatingfunctional}) and (\ref{eqn::moveddisorder}) is
	that we moved the term containing the quenched disorder into a separate exponential. Since our
	aim is to take an average over all possible realisations of this disorder, we will only need to
	focus on the last exponential which we rewrite as

@@

	It should be noted that we have changed some of the subscripts on the terms. Since these terms
	are all multiplied together and we sum over the subscripts, the letters we choose are of no
	importance and we can exchange them freely. We will define both exponentials in $Q$ as $Q_1$ and
	$Q_2$ respectively.

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run1.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2.png}
	\caption{$\alpha = 0.2$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2_Run_2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/tau_005.png}
	\caption{$\tau = 0.0$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/tau_015.png}
	\caption{$\tau = 0.15$}
	\end{subfigure}

@@

\end{document}

### 2020-06-12 Documents/ESA/sections/ShortTermGoals.tex
Updated Write Up and ESA

\begin{document}
    \section{Convergence and Chaos in Q-Learning Agents} \label{sec::Chaos_in_Q-Learning}
    \subsection{Research Summary} \label{sec::Research Summary}

@@

>>>>

\begin{document}
    \section{Convergence and Chaos in Q-Learning Agents} \label{sec::Chaos_in_Q-Learning}

    We begin by considering the evolution of learning with agents who follow a Q-Learning approach.
    Specifically, we look at characterising the stability of agents learning strategies. This
    technique was first carried out by Sanders et al \cite{Sanders}, in which the authors
    characterised the strategy evolution of agents who learn using an 'Experience Weighted
    Attraction' (EWA) algorithm, which is seen to be a strong representation of how people learn in
    games. The authors were able to determine the regions of parameter space in which learning is
    likely to converge towards stable equilibriums, as opposed to complex behaviours (such as limit
    cycles or chaotic dynamics). The aim of this study is to format these techniques for the study
    of computational agents who follow the popular Q-Learning approach \cite{SuttonBarto,Schwarz}.

    We aim, similarly, to determine the regions of parameter space in which the agents are likely to
    converge to stable equilibria. In this way it will be possible to, a priori, determine whether,
    for a particular game, the behaviour is likely to converge and even how to choose the agent or
    game parameters to ensure the predicatability of the resulting behaviour. To achieve this, we
    consult the Q-Learning Dynamics proposed by Tuyls et al \cite{TuylsDynamics}. In this study, the
    authors were able to derive a continuous time dynamical system describing how agents following a
    Q-Learning approach adjust the probabilities of choosing actions as they iteratively play a
    game. These equations are shown in \cite{TuylsDynamics} to accurately model the expected
    behaviour of agents as they iterate a game, and the experiments which verified this model are
    shown in \textbf{Figures ...} .

    With the accuracy of the continuous time dynamical system (\ref{eqn::EOM}) established, we analyse the
    stability of this system in the following section. Note that whilst the derivation provided is
    for the particular case of two agents for the sake of brevity, the problem of p-player games is
    equivalent to that of two players and so the solutions to the former can (and will) be
    presented.

    \subsection{Research Summary} % \subfile{./sections/ResearchSummary.tex} \label{sec::Research
    % Summary}

    \subsection*{Future Work} \label{sec::Future Work}

    As mentioned, the above system considers only a two player game. This was done with the intention
    of simplifying the notation and reducing the complexity of the experiments. However, the next
    immediate action is to present the equivalent solutions for the case of a general p-player game.
    We then seek to expand this study to a population of agents. For this, we will study the
    stability of the system presented by Leung et al \cite{Leung} which presents a mean-field model
    describing the evolution of learning of a population of Q-Learning agents who play co-operative
    games against one another. This last point is an important limitation - the derived dynamics
    will only consider populations who must co-operate with one another (i.e. the $\Gamma$ value of
    the game is one).

@@

    This section builds on the work described in \ref{sec::Swarm_Field_Control} and will be the next
    mode of inquiry upon the completion of the work described in \ref{sec::Chaos_in_Q-Learning}.
    Recall that Bellomo et al describe the evolution of the distribution of a 'collisionless' swarm
    through

    \begin{equation}
    \begin{align*}    
        \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
        = 0 \quad  (\Vec{x}, \Vec{v}) \in \Omega[f] \times D_{\Vec{v}}, \quad t>0, \\
        F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*.
    \end{align*}
    \end{equation}

    In this study we will attempt to formulate an optimal control problem in which the term $F_a[f]
    (t, \Vec{x}, \Vec{v})$ takes the role of the control input (we will likely choose a fixed value
    of $\psi$ to reduce complexity). Note that $F_a$ is dependent on the density function f and so
    we aim to apply feedback controls to the swarm.
